Extracting Maximum-Precision Radial Velocities from High-Resolution Spectra

### 2017-09-11 paper/paper.tex
syncing old changes, full order fitting

\title{How to Extract Maximum-Precision Radial Velocities from High-Resolution Spectra}

@@

Accurate spectroscopic measurements of radial velocities (RVs) have long been a critical tool across many subfields of astronomy, from galactic dynamics to cosmic expansion. In recent decades, however, a new focus has emerged on \textit{extremely precise} RV measurements of stars as a means of detecting exoplanets. For this application, measuring the absolute velocity of the star is much less important than resolving its changes through time. With sub-\ms-level precision required for the detection of Earth-like planets, vast amounts of effort have been poured into the engineering challenges of constructing a sufficiently stable spectrograph (or, failing that, being able to track the drift of a spectrograph over time) \todo{(cite some review papers)}. At the same time, great strides have been made towards disentangling true Doppler shifts from imitative signals like stellar pulsations and magnetic activity features \todo{(cite some review papers)}.  In this work, we investigate another fundamentally important but less commonly discussed aspect of the quest for maximum-precision RVs: the method of analysis used to extract the RV from a stellar spectrum.

@@

\section{Overview of Methods}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{binarymask}
\caption{Illustration of a weighted binary mask (blue windows) plotted over a small segment of the solar spectrum (black). The vertical length of each mask window scales to the square root of the weight given to the line when performing a cross-correlation between mask and spectrum.}
\label{fig:binarymask}
\end{figure}

>>>>

\title{Extracting Maximum-Precision Radial Velocities from High-Resolution Spectra}

@@

Accurate spectroscopic measurements of radial velocities (RVs) have long been a critical tool across many subfields of astronomy, from galactic dynamics to cosmic expansion. In recent decades, however, a new focus has emerged on \textit{extremely precise} RV measurements of stars as a means of detecting exoplanets. For this application, measuring the absolute velocity of the star is much less important than resolving its changes through time. With sub-\ms-level precision required for the detection of Earth-like planets, vast amounts of effort have been poured into the engineering challenges of constructing a sufficiently stable spectrograph (or, failing that, being able to track the drift of a spectrograph over time) \todo{(cite some review papers)}. At the same time, great strides have been made towards disentangling true Doppler shifts from imitative signals like the spectral signatures of stellar pulsations and magnetic activity features \todo{(cite some review papers)}.  In this work, we investigate another fundamentally important but less commonly discussed aspect of the quest for maximum-precision RVs: the method of analysis used to extract the RV from a stellar spectrum.

While the general idea of measuring a Doppler shift by the relative motions of stellar absorption lines is fairly straightforward, there are considerable subtleties to implementing this, from the choice of template

We begin in Section \ref{s:methods} with a summary of the practices used by current RV pipelines, including cross-correlation and template fitting. We then implement these techniques to extract RVs from a 5-\r{A} section of simulated spectrum and compare their performance in Section \ref{s:fakedata}.

@@

\section{Overview of Methods}
\label{s:methods}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{binarymask}
\caption{Illustration of a weighted binary mask (blue windows) plotted over a small segment of the solar spectrum (black). The vertical length of each mask window corresponds to the weight given to the line when performing a cross-correlation between mask and spectrum.}
\label{fig:binarymask}
\end{figure}
